Title

### 2023-05-04 paper/main.tex
Advancing paper

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{graphicx, caption}
\usepackage{authblk}
\usepackage{textcomp}

@@

\section*{Methods}

@@

@@

For each experiment/simulation, we extract the current front position as a function of time (see Fig. \ref{fig:fig3}).

>>>>

\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{graphicx, caption}
\usepackage{authblk}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsmath}

@@

\section{Methods}

@@

\paragraph{Set-up 1}

Specifications of IMFT set-up

\paragraph{Set-up 2}

Specifications of LEGI set-up

\paragraph{Set-up 3}

Specifications of LEMTA set-up

@@

For each experimental/numerical run, we extract the current front position as a function of time (see Fig. \ref{fig:fig3}a). A few selected runs are shown on figure~\ref{fig:fig3}b in non-dimensional time coordinates. After a short transient acceleration phase, most currents exhibit at first a constant velocity corresponding to the so-called \emph{slumping} regime. After this, the velocity can decrease, either because of settling induced buoyancy loss, or because the current enters the \emph{inertial} regime.

It can be qualitatively seen that increasing the bottom slope increases the slumping velocity, while increasing the Stokes number shortens the duration of the constant-velocity regime.
%
To properly quantify that, we fit all front propagation curves (except Dataset 4) with the following equation:

\begin{equation}
	\label{eq:fit_eq}
	\frac{x_{\rm f}}{L_{0}} = x_{i} + \mathcal{F}r \frac{t}{t_{0}} - \frac{\tilde{\lambda}}{2} \left(\frac{t}{t_{0}}\right)^{2},
\end{equation}
where $\mathcal{F}r$ corresponds now to the non-dimensional current velocity during the slumping regime, and $\tilde{\lambda}$ to the dissipation. The fit is performed between $t/t_{0} = 5$, to avoid the initial transient phase, and $t/t_{0} = 30$, the transition time from the slumping to the inertial regime~\citep{refs}. Note that $x_{i}$ is kept constant equal to 0 for Dataset 1, 2 and 3, but had to be left free to adjust for the SedFoam simulations \textcolor{red}{comment this}. For runs with strong dissipation ($\tilde{\lambda} > 2 {\times} 10^{-2}$), we add a quartic term to \eqref{eq:fit_eq} to improve the fit quality and obtain a better estimation of $\mathcal{F}r$ and $\tilde{\lambda}$. We checked that our results does not depend on the presence of this quartic term, and that the linear and quadratic ones remain much larger.

For Dataset 4, the time resolution as well as the experiment duration does not allow to extract the dissipation. Therefore, we simply fit the whole available points with a linear function.
